An Extendable \proglang{Python} Implementation of Robust Optimisation Monte Carlo

### 2022-02-20 article/latex_files/ch4/4-4-extensibility.tex
final version

The four replaceable parts described above, are solved using the four
methods of the \linebreak \code{OptimisatioProblem} class; (a)
\code{solve_gradients(**kwargs)}, (b) \code{solve_bo(**kwargs)},
\linebreak (c) \code{build_region(**kwargs)}, (d)
\code{fit_local_surrogate(**kwargs)}. The user can create a custom
class that inherits the basic \code{OptimisatioProblem} and, then,
overwrite any of the four functions with custom ones. Suppose a user
wants to fit Neural Networks as local surrogate models
\(\tilde{d}_i\). The user should overwrite the
\code{fit_local_surrogate(**kwargs)} function with one that internally
trains a neural network. In the following snippet we illustrate that,
using the \code{neural_network.MLPRegressor} class of the
\pkg{scikit-learn} package.

@@

In the same way, the user may replace each of the other three
functionalities. The only restriction that must be respected, concerns
the side-effects each method has at the \code{OptimisatioProblem}
class level. In the following four snippets we present the signature
of each method. We name the class-level variables that must be set
under the comment \code{\# side-effects}.

@@

% Let's say we have observed that the local area around $\theta_i^*$ is
% too complex to be represented by a simple quadratic model\footnote{as
%   in the current implementation}. Hence, the user selects a neural
% network as a good alternative. In the following snippet, we
% demonstrate how they could implement this enhancement without much
% effort; (a) they have to develop the neural network using the package
% of their choice (b) they must create a custom optimisation class which
% inherits the basic \code{OptimisationClass} and (c) they have to
% overwrite the \code{fit_local_surrogate} routine, with one that
% sets the neural network's prediction function as the
% \code{local_surrogate} attribute. The argument \code{**kwargs}
% may be used for passing all the important arguments, e.g.\ training
% epochs, gradient step etc. If, for example, they would like to set the
% size of the training set dynamically, we may replace \code{x =
%   self.regions[0].sample(30)} with \code{x =
%   self.regions[0].sample(kwargs["nof_examples"])}. Finally, they must
% pass the custom optimisation class, when calling the \code{ROMC}
% method.

% \begin{Code}
% ------------------------------ python snippet ------------------------------  
%   class NeuralNetwork:
%       def __init__(self, **kwargs):
%           # set the input arguments

%       def train(x, y):
%           # training code

%       def predict(x):
%           # prediction code

%   # Inherit the base optimisation class
%   class customOptim(elfi.methods.parameter_inference.OptimisationProblem):
%       def __init__(self, **kwargs):
%           super(customOptim, self).__init__(**kwargs)

%       # overwrite the function you want to replace
%       def fit_local_surrogate(**kwargs):
%           # init and train the NN
%           x = self.regions[0].sample(30) # 30 training points
%           y = [np.array([self.objective(ii) for ii in x])]
%           nn = NeuralNet()
%           nn.train(x,y)

%           # set the appropriate attribute
%           self.local_surrogate = nn.predict

%           # update the state
%           self.state["local_surrogate"] = True

%   # pass the custom inference method as argument
%   romc = elfi.ROMC(dist, bounds, custom_optim_class=customOptim)
% ----------------------------------------------------------------------------
% \end{Code}

>>>>

The four replaceable parts described above, are solved using the four
methods of the \linebreak \code{OptimisatioProblem} class; (a)
\code{solve_gradients(**kwargs)}, (b) \code{solve_bo(**kwargs)},
\linebreak (c) \code{build_region(**kwargs)}, (d)
\code{fit_local_surrogate(**kwargs)}. The user can create a custom
class that inherits the basic \code{OptimisatioProblem} and, then,
overwrite any of the four functions with custom ones. Suppose a user
wants to fit Neural Networks as local surrogate models
\(\tilde{d}_i\). The user should overwrite the
\code{fit_local_surrogate(**kwargs)} function with one that internally
trains a neural network. In the following snippet we illustrate how to
do that, using the \code{neural_network.MLPRegressor} class of the
\pkg{scikit-learn} package.

@@

In the same way, the user may replace each of the other three
functionalities. The only restriction that must be respected concerns
the side-effects each method has at the \code{OptimisatioProblem}
class level. In the following four snippets we present the signature
of each method and we name the class-level variables that must be set
under the comment \code{\# side-effects}.

@@
